### 2024-07-16 paper/tex/01-introduction.tex
WIP: fix references, add appendix

\paragraph*{Correctness of the algorithm (\cref{sec:proofs})}
  We prove that our algorithm is terminating and both sound and complete with
  respect to the declarative specification. This proof of soundness and completeness
  of the algorithm required us to introduce an intermediate system in-between
  the declarative and the algorithmic systems, and furthermore, the
  soundness and completeness proofs are mutually recursive with each other.
  The central theorems and the key proof ideas are formulated in \cref{sec:proofs}, 
  while the full definitions and formal proofs are deferred to the appendix (\cref{appendix}).

>>>>

\paragraph*{Correctness of the algorithm (\cref{sec:proofs})}
  We prove that our algorithm is terminating and both sound and complete with
  respect to the declarative specification. This proof of soundness and completeness
  of the algorithm required us to introduce an intermediate system in-between
  the declarative and the algorithmic systems, and furthermore, the
  soundness and completeness proofs are mutually recursive with each other.
  The central theorems and the key proof ideas are formulated in \cref{sec:proofs}, 
  while the full definitions and formal proofs are deferred to the appendix (\cref{appendix,app:proofs}).

### 2024-07-16 paper/tex/03-declarative-system.tex
WIP: fix references, add appendix

The normalization algorithm is shown in \cref{fig:type-nf}. The steps (i-ii) are
implemented by the \emph{ordering} function `$[[ord varset in iN]]$' and `$[[ord
varset in iP]]$'. For a set of variables $[[varset]]$ and a type, it returns a
list of variables from $[[varset]]$ that occur in the type in the \emph{order of
their first occurrence}. For brevity, we omit the formal definition of ordering
referring the reader to the appendix (\cref{appendix}).

@@

For brevity, we omit the formal definition of the term-level elaboration,
referring the reader to the appendix (\cref{sec:term-translation}). We define
the elaboration in such a way that it preserves the soundness invariants given
in \cref{tab:elaboration-soundness}.

>>>>

The normalization algorithm is shown in \cref{fig:type-nf}. The steps (i-ii) are
implemented by the \emph{ordering} function `$[[ord varset in iN]]$' and `$[[ord
varset in iP]]$'. For a set of variables $[[varset]]$ and a type, it returns a
list of variables from $[[varset]]$ that occur in the type in the \emph{order of
their first occurrence}. For brevity, we omit the formal definition of ordering
referring the reader to the appendix (\cref{alg:var-ordering}).

@@

For brevity, we omit the formal definition of the term-level elaboration,
referring the reader to the appendix (\cref{sec:term-level-translation}). We define
the elaboration in such a way that it preserves the soundness invariants given
in \cref{tab:elaboration-soundness}.

### 2024-07-16 paper/tex/06-extensions.tex
WIP: fix references, add appendix

    % \paragraph*{Restricting Inference}
    Instead, we strengthen
    \ruleref{\ottdruleATArrowAppBidirLabel}
    in such a way that it never checks a term against an algorithmic type. Type
    checking $[[v]]$ against $[[uQ]]$ is replaced by a more restrictive
    premise---checking that $[[v]]$ \emph{synthesizes a subtype} of $[[uQ]]$:
    $$ \ottdruleATArrowAppBidirSLabeled{} $$\\

    As one can expect, the declarative rule is also changed accordingly.
    In terms of practicality, this change disallows
    implicit checking against a \emph{polymorphic} type:
    $[[·;· ⊢ λx.return x ⇐ ∀α⁺.α⁺ → ↑α⁺]]$ is not allowed, because
    it would require adding algorithmic $[[x:α̂⁺]]$ to the context.
    However, once the instantiation is made explicit or the lambda is explicitly 
    polymorphic, the checking is allowed:
     $[[·;· ⊢ λx.return x ⇐ Int → ↑Int]]$ and 
     $[[·;· ⊢ Λα⁺.λx:α⁺.return x ⇐ ∀α⁺.α⁺ → ↑α⁺]]$ are both valid.

>>>>

    % \paragraph*{Restricting Inference}
    Instead, we strengthen
    \ruleref{\ottdruleATArrowAppBidirLabel}
    in such a way that it never checks a term against an algorithmic type. Type
    checking $[[v]]$ against $[[uQ]]$ is replaced by a more restrictive
    premise---checking that $[[v]]$ \emph{synthesizes a subtype} of $[[uQ]]$:
    $$ \ottdruleATArrowAppBidirSLabeled{} $$
    As one can expect, the declarative rule is also changed accordingly.
    In terms of practicality, this change disallows
    implicit checking against a \emph{polymorphic} type:
    $[[·;· ⊢ λx.return x ⇐ ∀α⁺.α⁺ → ↑α⁺]]$ is not allowed, because
    it would require adding algorithmic $[[x:α̂⁺]]$ to the context.
    However, once the instantiation is made explicit or the lambda is explicitly 
    polymorphic, the checking is allowed:
     $[[·;· ⊢ λx.return x ⇐ Int → ↑Int]]$ and 
     $[[·;· ⊢ Λα⁺.λx:α⁺.return x ⇐ ∀α⁺.α⁺ → ↑α⁺]]$ are both valid.
